Make manuscript figures

### 2022-05-30 scripts/R/make_manuscript_figures.rmd
adjust sim results fig alignment

top_row <- plot_grid(NULL, rmse_plot, rel_widths = c(1, 3.25), labels = c("", "A"))
png(filename = "figures/simulation_results.png", width = linewidth, height = height, unit = "cm", res = 300)
plot_grid(top_row, tpr_plot, align = "v", axis = "tb", nrow = 2, labels = c("", "B"))
dev.off()
```

>>>>

top_row <- plot_grid(NULL, rmse_plot, rel_widths = c(1.03, 3), labels = c("", "A"))
png(filename = "figures/simulation_results.png", width = linewidth, height = height, unit = "cm", res = 300)
plot_grid(top_row, tpr_plot, align = "v", axis = "tb", nrow = 2, labels = c("", "B"))
dev.off()
```
